Dynamic Transition Analysis with TIMES

### 2020-06-17 doc/2020-03-paper/methods.tex
completed economic data table (first draft)
Former-commit-id: 11d12709b9a7acbddcc4268ef9157a0b7255b47b
Former-commit-id: 1fd4530b8cc901f3c87c966b8dd760ec7c84af26

\begin{landscape}
\begin{longtable}{ |*{8}{c|} }
\caption{Economic data for modelled technologies.}\\
\hline
\textbf{Technology} & \textbf{Capital} & \textbf{Fixed} & \textbf{Variable} & \textbf{Lifespan} & \textbf{Capacity Factor/} & \textbf{Emission} & \textbf{Year} \\
\textbf{name} & \textbf{Cost} & \textbf{\gls{OM}} & \textbf{\gls{OM}} &  & \textbf{Efficiency} & \textbf{Coefficient} & \textbf{available} \\
 & MUSD/GW & MUSD/GW & MUSD/GWh & Years  &  & gCO$_2$/kWh  &  \\
\hline
\endhead  % header material
\hline
\endfoot  % footer material
\hline
\endlastfoot
\gls{USC} & 3661 & 40.41 & 4.48 & 40 & CF=0.55 & 943 & 2017 \\
\gls{lng} & 1079 & 14 & 2.54 & 30 & CF=0.55 & 599 & 2017 \\
Nuclear & 6317 & 121.13 & 2.36 & 60 & CF=0.6-0.95 & 943 & 2017 \\
Li-ion Storage & 1876 (2017) & 10 & 0.3 & 10 & Eff=0.86 & 52 & 2017 \\
 & 1446 (2025) &  &  &  &  & &  \\
Solar & 1307(2017) & 15.19 & 0  & 25 & CF=0.14 & 37 & 2017 \\
 & 1086(2040) & & & & &  & \\
 & 615(2050) & & & & & &  \\
Onshore Wind & 3454(2017) & 136.37 & 0 & 25 & CF=0.25(2017) & 20(2017) & 2017 \\
 & 3110(2040) &  &  &  & CF=0.3(2040) & 7(2040) &  \\
 & 2800(2050) &  &  &  & CF=0.35(2050) &  &  \\
Offshore Wind(Fixed) & 7772(2017) & 341 & 0 & 25 & CF=0.3(2017) & 25(2017) & 2017 \\
 & 5438(2040) &  &  & & CF=0.35(2040) & 11(2040) &  \\
 &  &  &  & & CF=0.4(2050) &  &  \\
Offshore Wind(Floating) & 12897(2017) & 423 & 0 & 25 & CF=0.35(2017) & 25(2017) & 2017 \\
 & 9023(2040) &  &  &  & CF=0.4(2040) & 11(2040)  &  \\
 &  &  &  &  & CF=0.45(2050) &  &  \\
CCS-LNG(90\%) & 5088(2022) & 33(2022) & 0.0631(2022) & 30 & CF=0.12-0.4(2017) & 42(2022) & 2022 \\
 & 2313(2050) & 14(2050) & 0.044(2050) &  & CF=0.35(2017) &  & \\
CCS-USC(90\%) & 6816(2023) & 84(2023) & 0.093(2023) & 40 & CF=0.27-0.3(2017) & 94.3(2022) & 2023 \\
 & 3552(2050) & 69(2050) & 0.058(2050) &  &  &  & \\
Emerging Solar & 4600(2017) & 15.19(2017) & 0 & 25 & Eff=0.22(2017) & 22(2017) & 2017 \\
 & 4600(2017) & 15.19 & 0 & 25 & Eff=0.22(2017) & 22(2017) & 2017 \\
 & 3822(2030) &  &  &  & Eff=0.25(2025) &  13(2040) &  \\
 & 2164(2035) &  &  &  & Eff=0.3(2030) &  &  \\
  & 1086(2040) &  &  &  &  &  &  \\
 & 615(2050) &  &  &  &  &  &  \\
  & 600(2051) &  &  &  &  &  &  \\
\gls{PEMFC} & 7399(2022) & 30.65 & 0.59 & 7 (CF=0.9) & Eff=0.6 & 0.408(2022) & 2022\\
 & 4000(2030) &  &  &  &  & 0.245(2030) &  \\
 & 3000(2030) &  &  &  &  & 0.245(2030) &  \\
\gls{AEC} & 1500(2022) & 6.87 & 0.0009 & 10(CF=0.9) & Eff=0.82 & 3.19 & 2022\\
 & 850(2030) &  &  &  &  & &  \\
\gls{PEMEC} & 3500(2022) & 30.65 & 0.006 & 7 (CF=0.9) & Eff=0.78(2022) & 38.17(2022) & 2022\\
 & 2200(2025) &  &  &  &  & 16(2050) &  \\
 & 1500(2030) &  &  &  &  &  &  \\
 & 1000(2035) &  &  &  &  &  &  \\
 & 500(2040) &  &  &  &  &  &  \\
\gls{SOEC} & 3500(2022) & 30.65 & 0.006 & 7 (CF=0.9) & Eff=0.78(2022) & 38.17(2022) & 2050\\
\gls{SOFC} & 3500(2022) & 30.65 & 0.006 & 7 (CF=0.9) & Eff=0.78(2022) & 38.17(2022) & 2030\\
\gls{PWS} & 3500(2022) & 30.65 & 0.006 & 7 (CF=0.9) & Eff=0.78(2022) & 38.17(2022) & 2050\\
\label{eco}
\end{longtable}
\end{landscape}

>>>>

\begin{landscape}
\begin{longtable}{ |*{8}{c|} }
\caption{Economic data for modelled technologies.}\\
\hline
\textbf{Technology} & \textbf{Capital} & \textbf{Fixed} & \textbf{Variable} & \textbf{Lifespan} & \textbf{Capacity Factor/} & \textbf{Emission} & \textbf{Year} \\
\textbf{name} & \textbf{Cost} & \textbf{\gls{OM}} & \textbf{\gls{OM}} &  & \textbf{Efficiency} & \textbf{Coefficient} & \textbf{available} \\
 & MUSD/GW & MUSD/GW & MUSD/GWh & Years  &  & gCO$_2$/kWh  &  \\
\hline
\endhead  % header material
\hline
\endfoot  % footer material
\hline
\endlastfoot
\gls{USC} & 3661 & 40.41 & 4.48 & 40 & CF=0.55 & 943 & 2017 \\
\gls{lng} & 1079 & 14 & 2.54 & 30 & CF=0.55 & 599 & 2017 \\
Nuclear & 6317 & 121.13 & 2.36 & 60 & CF=0.6-0.95 & 943 & 2017 \\
Li-ion Storage & 1876 (2017) & 10 & 0.3 & 10 & Eff=0.86 & 52 & 2017 \\
 & 1446 (2025) &  &  &  &  & &  \\
Solar & 1307(2017) & 15.19 & 0  & 25 & CF=0.14 & 37 & 2017 \\
 & 615(2050) & & & & & &  \\
Onshore Wind & 3454(2017) & 136.37 & 0 & 25 & CF=0.25(2017) & 20(2017) & 2017 \\
 & 2406(2050) &  &  &  & CF=0.35(2050) &  &  \\
Offshore Wind(Fixed) & 7772(2017) & 341 & 0 & 25 & CF=0.3(2017) & 25(2017) & 2017 \\
 & 3381(2050) &  &  & & CF=0.40(2050) &  &  \\
Offshore Wind(Floating) & 12897(2017) & 423 & 0 & 25 & CF=0.35(2017) & 25(2017) & 2017 \\
 & 5610(2050) &  &  &  & CF=0.45(2050) &  &  \\
CCS-LNG(90\%) & 2626(2022) & 27.484 & 0.0531 & 30 & CF=0.12-0.4(2017) & WHA & 2022 \\
 & 1422(2050) &  & &  &  &  & \\
CCS-USC(90\%) & 5252(2023) & 59 & 0.094 & 40 & CF=0.27-0.3(2017) & 94.3(2022) & 2023 \\
 & 4091(2050) &  &  &  &  &  & \\
Emerging Solar & 4600(2017) & 15.19 & 0 & 25 & Eff=0.22(2017) & 22(2017) & 2017 \\
  & 600(2050) &  &  & Eff=0.3(2030) &  & 13(2040) &  \\
\gls{AEC} & 1500(2022) & 8 & 0.0004 & 11(CF=0.9) & Eff=0.7 & 1.29 & 2022\\
 & 850(2030) &  &  &  &  & &  \\
\gls{PEMEC} & 3500(2022) & 8 & 0.0004 & 7 (2022)(CF=0.9) & Eff=0.75(2022) & 8.7(2022) & 2022\\
 & 1500(2030) &  & 11(2050)  &  & Eff=0.82(2030) & 0.456(2050)  &  \\
 & 400(2050) &  &  &  & &  &  \\
\gls{SOEC} & 6000(2030) & 8 & 0.0004 & 2 (2030)(CF=0.9) & Eff=0.9 & 5.4(2030) & 2030\\
 & 1000(2050) &  &  & 7 (2050) &  & 1.08(2050) & \\
 & 400(2070) &  &  & 11 (2070) &  & 0.72(2070) & \\
Gas Reforming & 763 & 6.21 & 0.04 & 30  & Eff=0.7 & 400 & 2022\\
Gas Reforming w/ CCS & 1200 & 8 & 0.077 & 30 & Eff=0.5 & 120 & 2022\\
\gls{PEMFC} & 7399(2022) & 30.65 & 0.59 & 7 (CF=0.9) & Eff=0.49 & 1.087(2022) & 2022\\
 & 4000(2030) &  &  &  &  & 0.65(2030) &  \\
 & 3000(2035) &  &  &  &  &  &  \\
\gls{SOFC} & 7399(2030) & 30.65 & 0.59 & 10 (CF=0.9) & Eff=0.7 & 2.11(2030) & 2030\\
 & 4000(2035) &  &  &  &  & 1.27(2040) &  \\
 & 3000(2040) &  &  &  &  & &  \\
\gls{PWS} & 14706  & 236.5 & 0 & 20(CF=0.9) & Eff=0.15(2050) & Unknown & 2050
\label{eco}
\end{longtable}
\end{landscape}
